\documentclass[a4paper]{letter}
\usepackage[super]{nth}
\signature{Daniel Winz}
\address{
    Mangelegg 134 \\
    6430 Schwyz \\
    Switzerland}
\begin{document}
\begin{letter}{
    Mrs. Petruschka Meyer \\
    Lucerne University of Applied Sciences and Arts \\
    Engineering \& Architecture \\
    Technikumstrasse 21 \\
    CH-6048 Horw \\
    Switzerland}
\opening{Dear Mrs. Meyer}
%Introduction
I am writing to tell you some hopefully interesting things about my 
professional background and my studies. 

% your course of studies
I study electrical engineering. Currently I'm in the \nth{8} semester. 

% your professional background: apprenticeships and / or internships, work 
% experience
During the studies I work part time in medical engineering at Schiller AG. 
Before the studies I did an apprenticeship as electronics engineer at Siemens. 

% English language foundations including travel, studies and / or work abroad
I had English course during school and my apprenticeship. During the 
apprenticeship I passed the FCE and was two weeks in Oxford to learn English. 

% your particular interests in the course: 
%%% Which of the lexical topics listed in the course agenda are you 
%%% particularly interested in? 
From the course agenda I am most interested in figures, graphs and trends. 
This is because as electrical engineering I will often work with them. 
Therefore it can be important to describe these in English. 
%%% What do you especially wish to improve (reading, speaking, range of 
%%% vocabulary, confidence in grammar, writing) and why?
I would like to improve reading as this is what I will do most of the time in 
my job. 

% projects and main topics you are working on currently, this semester
Last semester I got involved in the AMZ (Academic Motorsports Club Zurich). 
The AMZ designs a racing car every year for the formula student competition. 
As we design the wheel hub motors ourselves we have a test bench for these. 
Currently I am working on the improvement of the motor test bench in matters 
of safety an reliability. For my bachelor thesis I am going to work on a new 
inverter. An inverter converts the direct current from the accumulator into 
three-phase alternating current for the motors. 

% your academic and professional interests and goals
I am going to finish my undergraduate studies in one year. Afterwards I would 
like to work in research or development. 

% Ending
I am looking forward to an interesting semester. 

\closing{Kind regards,}
\end{letter}
\end{document}
